Synthesis of Linear Functional Programs

### 2021-05-09 article/article.tex
tweaks

% \section{Separate}

% More about the concepts than citing concrete works (but citations are
% needed!):
% \begin{enumerate}
% \item PL/Type systems in a ``formal'' sense (inference rules, etc) [DONE]
% \item Propositions as types: Proofs as programs, proof search as
%   synthesis, etc. [MOSTLY DONE]
% \item Linear logic: a ``resource aware logic'' [ONGOING]
% \item Proof search in LL: challenges, focusing as a ``solution'' [ONGOING]
% \item Linear $\lambda$-calculus: what does it look like.
% \item Type-based synthesis: ``inverting'' a type system.
% \end{enumerate}

@@

\mypara{Work Plan}
The end goal is to have a synthetizer capable of taking a type (possibly refined) as input,
and to produce (possibly interactively) a function or more (possibly recursive) with that same type.
We've already created a parser and a type-checker -- more than good preparation for the
development of the synthetizer, they will be useful to \emph{validate} the functions synthetized, and to implement the
synthesis of partial programs. The implementations are in Haskell, a functional language, since it's easier to reason about inference rules that way.

>>>>

@@

\mypara{Work Plan}
The end goal is to have a synthetizer capable of taking a type (possibly refined) as input,
that produces (possibly interactively) a function or more (possibly recursive) with that same type.
We've already created a parser and a type-checker -- more than good preparation for the
development of the synthetizer, they will be useful to \emph{validate} the functions synthetized, and to implement the
synthesis of partial programs. The implementations are in Haskell, a functional language, since it's easier to reason about inference rules that way.
Our work began
